---
title: "Guide-to-OutlierdectionCompstat"
output: rmarkdown::html_vignette
fig_width: 6
fig_height: 4
vignette: >
  %\VignetteIndexEntry{Guide-to-OutlierdectionCompstat}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This packages attempts to find outliers based on the number of standard deviations. It includes a plot summary and print method aswell as the S3 object Outliervec

```{r setup,echo=FALSE,out.width=c('500px')}
library(OutlierdetectionCompstat)
```

The package assume that the data comes in the form of a vector. Below we have generated 100 standard normally distributed r.vs 

```{r,echo=FALSE,fig.width=6,fig.height=4,fig.show="hold", fig.align="center"}
set.seed(1000)
vector<- rnorm(100)
```

Below we have plotted this dataset. 
```{r,echo=FALSE,fig.width=6,fig.height=4,fig.show="hold", fig.align="center"}
plot(vector,ylab="")
```


The packages attempts to discover outliers based on the number of standard deviations observations are away from the mean. As a default option it detects outliers that are more than 2 standard deviations away. The package uses the observed mean and observed standard deviation.

```{r,echo=FALSE,fig.width=6,fig.height=4,fig.show="hold", fig.align="center"}
Outliers<-OutlierVec(vector)
Outliers
```
The package has found 5 potential outliers. More details can be shown using the summary function.

```{r,echo=FALSE,fig.width=6,fig.height=4,fig.show="hold", fig.align="center"}
Outliers<-OutlierVec(vector)
summary(Outliers)
```

It also includes a plot function, which can be seen below.

```{r,echo=FALSE,fig.width=6,fig.height=4,fig.show="hold", fig.align="center"}
Outliers<-OutlierVec(vector)
plot(Outliers)
```
